Clustering analysis and statistics

### 2019-03-27 notebooks/Clustering analysis.Rmd
removed erroneous mean values from plot

# Run functions
summary_stats <- run_df %>%
  mutate(total_mean = round(mean(value)*100, 3)) %>%
  group_by(group1) %>%
  mutate(mean = round(mean(value)*100, 3),
         var = round(var(value)*100, 3)) %>%
  select(group1, total_mean, mean, var) %>%
  summarise_all(funs(func_paste))

summary_stats2 <- run_df %>%
  mutate(total_mean = round(mean(value), 3)) %>%
  group_by(group1) %>%
  mutate(mean = round(mean(value), 3),
         var = round(var(value), 3)) %>%
  select(group1, total_mean, mean, var) %>%
  summarise_all(funs(func_paste))

@@

@@

ggplot(complete_data, aes(Percent)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.2, color = "black",
                fill = "grey80") +
  stat_function(fun = dnorm,
                args = with(complete_data, c(mean = mean(Percent), sd = sd(Percent))),
                color = "red") +
  geom_segment(aes(x = complete_data$Percent[1],
                   xend = complete_data$Percent[1], y = 0.08, yend = 0),
               arrow = arrow(length = unit(0.3, "cm"),
                             type = "closed"),
               color = "#4575b4") +
  geom_segment(aes(x = complete_data$Percent[2],
                   xend = complete_data$Percent[2], y = 0.08, yend = 0),
               arrow = arrow(length = unit(0.3, "cm"),
                             type = "closed"),
               color = "#74add1") +
  geom_segment(aes(x = complete_data$Percent[3],
                   xend = complete_data$Percent[3], y = 0.08, yend = 0),
               arrow = arrow(length = unit(0.3, "cm"),
                             type = "closed"),
               color = "#f46d43") +
  geom_segment(aes(x = complete_data$Percent[4],
                   xend = complete_data$Percent[4], y = 0.08, yend = 0),
               arrow = arrow(length = unit(0.3, "cm"),
                             type = "closed"),
               color = "#fdae61") +
  geom_text(label = "p < 0.001",
            x = 83.30,
            y = 0.16,
            angle = 90) +
  geom_vline(xintercept = as.numeric(summary_stats$mean[1]),
             size = 1,
             color = "#4575b4") +
  geom_vline(xintercept = as.numeric(summary_stats$mean[2]),
             size = 1,
             color = "#74add1") +
  geom_vline(xintercept = as.numeric(summary_stats$mean[3]),
             size = 1,
             color = "#f46d43") +
  geom_vline(xintercept = as.numeric(summary_stats$mean[4]),
             size = 1,
             color = "#fdae61") +
  labs(x = "Percent (%) distances < 0.1 or > 0.8",
       y = "Density") +
  ggtitle(label = "Distribution of percentages",
          subtitle = "Number of iterations: 1000") +
  theme(plot.title = element_text(hjust = 0))

@@

summary_stats2

>>>>

# Run functions
summary_stats <- run_df %>%
  mutate(total_mean = round(mean(value), 3)) %>%
  group_by(group1) %>%
  mutate(mean = round(mean(value), 3),
         var = round(var(value), 3)) %>%
  select(group1, total_mean, mean, var) %>%
  summarise_all(funs(func_paste))

@@

summary_stats

@@

ggplot(complete_data, aes(Percent)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.2, color = "black",
                fill = "grey80") +
  stat_function(fun = dnorm,
                args = with(complete_data, c(mean = mean(Percent), sd = sd(Percent))),
                color = "red") +
  geom_segment(aes(x = complete_data$Percent[1],
                   xend = complete_data$Percent[1], y = 0.08, yend = 0),
               arrow = arrow(length = unit(0.3, "cm"),
                             type = "closed"),
               color = "#4575b4") +
  geom_segment(aes(x = complete_data$Percent[2],
                   xend = complete_data$Percent[2], y = 0.08, yend = 0),
               arrow = arrow(length = unit(0.3, "cm"),
                             type = "closed"),
               color = "#74add1") +
  geom_segment(aes(x = complete_data$Percent[3],
                   xend = complete_data$Percent[3], y = 0.08, yend = 0),
               arrow = arrow(length = unit(0.3, "cm"),
                             type = "closed"),
               color = "#f46d43") +
  geom_segment(aes(x = complete_data$Percent[4],
                   xend = complete_data$Percent[4], y = 0.08, yend = 0),
               arrow = arrow(length = unit(0.3, "cm"),
                             type = "closed"),
               color = "#fdae61") +
  geom_text(label = "p < 0.001",
            x = 83.30,
            y = 0.16,
            angle = 90) +
  labs(x = "Percent (%) distances < 0.1 or > 0.8",
       y = "Density") +
  ggtitle(label = "Distribution of percentages",
          subtitle = "Number of iterations: 1000") +
  theme(plot.title = element_text(hjust = 0))

@@
